From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/introduction.tex

In \lv, the choice of a particular name for an object is a ubiquitous problem---it underlies virtually all tasks that model how speakers use language to refer to objects in the world, such as image description, visual question answering and referring expression generation.
\lv methods are generally based on object detection or image classification models from computer vision (CV) research (or the visual features extracted from them) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (e.g., \name{bus}) while others seem overly specific (e.g.,\ \name{goblet, gyromitra}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs. slightly pointed). 
But it raises the issue of whether these models could be directly used for more human-like object naming.
% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.

>>>>

In \lv, object naming underlies virtually all tasks that model how speakers refer to objects in the world, such as image description or visual question answering.
\lv methods are generally based on object detection or image classification models from computer vision (CV) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others seem overly specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs. slightly pointed). 
But it raises the issue of whether these models could be directly used for more human-like object naming.
% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.
